\begin{frame}{Example 20 - Problem (1)}
Olé Oil produces three products: heating oil, gasoline, and jet fuel. The
average octane levels must be at least 4.5 for heating oil, 8.5 for gas and
7.0 for jet fuel. To produce these products Olé purchases two types of oil:
crude 1 (at \$12 per barrel) and crude 2 (at \$10 per barrel). Each day, at
most 10000 barrels of each type of oil can be purchased.
\end{frame}

\begin{frame}{Example 20 - Problem (2)}
Before crude can be used to produce products for sale it must be distilled.
Each day, at most 15000 barrels of oil can be distilled. It cost 10\$ to distill
a barrel of oil. The result of distillation is as follows: (1) Each barrel of
crude 1 yields 0.6 barrel of naphtha, 0.3 barrel of distilled 1, and 0.1 barrel
of distilled 2. (2) Each barrel of crude 2 yields 0.4 barrel of naphtha, 0.2
barrel of distilled 1, and 0.4 barrel of distilled 2. Distilled naphtha can be
used only to produce gasoline or jet fuel. Distilled oil can be used to produce
heating oil or it can be sent through the catalytic cracker (at a cost of 15\$
per barrel). Each day, at most 5000 barrels of distilled oil can be sent
through the cracker.
\end{frame}

\begin{frame}{Example 20 - Problem (3)}
Each barrel of distilled 1 sent through the cracker yields
0.8 barrel of cracked 1and 0.2 barrel of cracked 2. Each barrel of distilled 2
sent through the cracker yields 0.7 barrel of cracked 1 and 0.3 barrel of
cracked 2. Cracked oil can be used to produce gasoline and jet fuel but no to
produce heating oil.\\
\vspace{3mm}
The octane level of each type of oil is as follows: naphtha, 8; distilled 1, 4;
distilled 2, 5; cracked 1, 9; cracked 2, 6. \\
\vspace{3mm}
All heating oil produced can be sold at \$14 per barrel; all gasoline produced,
\$18 per barrel; and all jet fuel produced \$16 per barrel. Marketing
considerations dictate that at least 3000 barrels of each product must be
produced daily. Formulate an LP to maximize Olé’s daily profit.
\end{frame}
